Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-02 paper/src/paper.tex
table input.

In order to simulate how the simulation strategy for selecting policies would
work on non simulated traces, we randomly introduce noise in the estimate of
the waiting time defined by Eq.~\ref{eq:cost-exact} by rescaling it, either
down or up, for each job:
%
\begin{equation} \label{eq:cost-noisy} w_{\mbox{noisy}}(t;P_i) =
\sum_{j=1}^{l(\Delta_t)} \rho_j \, \mbox{Wait}_j^{P_i} \end{equation}
%
where $\rho$ is uniformly sampled in the interval $[0.85,1.15]$, thus adding a
+/-15\% noise on the waiting time estimated by the simulator. The overall cost
is then defined in the same way as before, leading to:
%
\begin{equation} \label{eq:tot-cost-noisy} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w_{\mbox{noisy}}(t;P_i) \end{equation}
%
As before (see Eq.~\ref{eq:select-exact}), the policy that minimizes the above
cost is selected for the period $\Delta_T$.

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement with respect to EASY-FCFS of fixed policies.}
  \label{tab:strat}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & Random &      & Full &      & Noisy &      & Bandit &     \\
    \hline
    $\Delta$     & day    & week & day  & week & day   & week & day    & week\\
    CTC-SP2      & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    SDSC-SP2     & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    SDSC-BLUE    & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    ANL-Intrepid & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    CEA-Curie    & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    Unilu-Gaia   & LCFS   & LPF  & SPF  & LQF  & SQF   & SEXP & LEXP   & LRF \\
    \hline
  \end{tabular}
\end{table*}

>>>>

In order to simulate how the simulation strategy for selecting policies would
work on non simulated traces, we randomly introduce noise in the estimate of
the policy cost defined by Eq.~\ref{eq:cost-exact} by rescaling it, either
down or up:
%
\begin{equation} \label{eq:cost-noisy} w_{\mbox{noisy}}(t;P_i) =
 \rho \sum_{j=1}^{l(\Delta_t)} \, \mbox{Wait}_j^{P_i} \end{equation}
%
where $\rho$ is uniformly sampled in the interval $[0.80,1.20]$, thus adding a
+/-20\% noise on the waiting time estimated by the simulator. The overall cost
is then defined in the same way as before, leading to:
%
\begin{equation} \label{eq:tot-cost-noisy} w(\rightarrow T;P_i) =
\sum_{t=0}^{T-1} \lambda^{T-1-t} w_{\mbox{noisy}}(t;P_i) \end{equation}
%
As before (see Eq.~\ref{eq:select-exact}), the policy that minimizes the above
cost is selected for the period $\Delta_T$.

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement with respect to EASY-FCFS of fixed policies.}
  \label{tab:strat}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & Random &      & Full &      & Noisy &      & Bandit & \\
    \hline
    $\Delta$     & day    & week & day  & week & day   & week & day    & week\\
    CTC-SP2      & -20    &      & -44  &      & -44   &      & -26    & \\
    KTH-SP2      & -6     &      & -12  &      & -12   &      & -7     & \\
    SDSC-SP2     & -4     &      & -13  &      & -13   &      & -5     & \\
    SDSC-BLUE    & -12    &      & -31  &      & -30   &      & -12    & \\
    ANL-Intrepid & -13    &      & -22  &      & -19   &      & -13    & \\
    CEA-Curie    & -35    &      & -53  &      & -53   &      & -36    & \\
    Unilu-Gaia   & -29    &      & -59  &      & -58   &      & -33    & \\
    \hline
  \end{tabular}
\end{table*}
